% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % 中英双语版，需要中文字体支持
\usepackage{linespacing_fix}
\usepackage{cite}

\begin{document}
\pagenumbering{gobble}

% ===================== 第一页：中文简历 =====================

\name{侯汶政｜Go后端工程师}

\section{\faInfoCircle\ 基本信息}
\vspace{0.5ex} % 增加一点间距避免拥挤
\begin{center}
\begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}}
    \textbf{个人网站：}\href{https://Soofjan.com}{Soofjan.com}\\
    
    \textbf{微信：}1489938120          & \textbf{当前状态：}深圳在职 \\
    \textbf{邮箱：}Soofjan1489938120@gmail.com & \textbf{到岗时间：}\textbf{2周} \\
    \textbf{学历：}本科全日制（\textbf{学信网可查}） & \textbf{求职偏好：}不外包 / 不驻场 \\
\end{tabular}
\end{center}

\section{\faCogs\ 技术能力}
\begin{itemize}[parsep=0.3ex]
    \item \textbf{编程语言与框架}：使用 Go（Gin、Gorm） 开发，系统掌握 关键字、并发、GMP 调度、内存管理等知识；拥有 Vue 实战经验，具备多端适应能力。
    \item \textbf{数据存储与缓存}：掌握 MySQL 存储引擎（InnoDB）、B+ 树索引、锁与事务（ACID、隔离级别、MVCC）；掌握 Redis 底层数据结构以及内部实现，熟悉过期策略、持久化、缓存等相关问题。
    \item \textbf{中间件}：熟悉 NSQ 架构，能处理消息丢失与重复消费；了解Kafka、RocketMQ等消息队列在不同场景下的使用选择。
    \item \textbf{开发工具}：熟悉 Git/Linux 开发环境；熟悉 TCP/IP、HTTP/HTTPS 等网络基础；高效使用 Cursor AI 工具。
\end{itemize}

\section{\faGraduationCap\ 教育背景}
\datedsubsection{\textbf{广州大学} \quad 学士，计算机科学与技术}{2019.09 -- 2023.06}
CET-6 英语六级（602分），全国大学生算法设计与编程挑战赛（银奖）

\section{\faSuitcase\ 工作经历}
\datedsubsection{\textbf{软件工程师 @ 慧为智能科技有限公司}}{2023.05 - 至今}

\paragraph*{私有云存储系统（NAS）开发}

\begin{itemize}

    \item \textbf{云端}：
    \begin{itemize}
        \item 主导设计 NAT 穿透交互架构，规范客户端、服务端、云端及穿透端的通信流程，实现复杂网络下稳定高效访问。
        \item 引入 NSQ 消息队列，实现事件异步解耦，提升吞吐1.6倍，高并发平均延迟降低约 50\%。
        \item 采用应用层 AES+RSA 和传输层 TLS 的双层加密方案，保障凭证与敏感字段在复杂网络下的传输安全。
    \end{itemize}

    \item \textbf{智能文档中心}：
    \begin{itemize}
        \item 针对内存受限环境，完成了从 Elasticsearch 到 Bleve 的搜索引擎迁移，结合 GPT 实现快速的全文与多维度检索。
        \item 设计基于块的索引策略与搜索结果聚合算法，解决超长文档索引阶段内存占用过高问题，峰值 heapInuse 降幅约 76\%+。
    \end{itemize}
    
    \item \textbf{文件索引同步系统}：
    \begin{itemize}
        \item 自研 BFS+Queue 架构替代 fsnotify 监听，在海量文件场景下内存开销降低 90\% 以上。
        \item 基于接口抽象与 Functional Options 模式，实现同步逻辑与底层存储、IO 的深度解耦，支持跨项目的高内聚集成。
    \end{itemize}
    
    \item \textbf{其他}：
    \begin{itemize}
        \item AI相册: 在RKNN平台上基于 JNI 封装实现标签分类；通过 DBSCAN 聚类算法实现万级人脸库的无监督聚类，支持动态聚类中心更新，识别准确率达 97.3\%。
        \item 通过 rate 限流、Ristretto 缓存库的方式有效缓解并发流量冲击，核心接口缓存命中率达 85\%，响应时间缩短 90ms。
        \item 开发并维护 Docker、虚拟机、Webdav 等前后端项目，提供 NAS 生态支持。
    \end{itemize}

\end{itemize}

% ===================== 第二页：英文简历 =====================
\newpage

\name{Wenzheng Hou | Go Backend Engineer}

\section{\faInfoCircle\ Basic Information}
\vspace{0.5ex}
\begin{center}
\begin{tabular}{p{0.45\textwidth} p{0.45\textwidth}}
    \textbf{Website: }\href{https://Soofjan.com}{Soofjan.com}\\
    
    \textbf{WeChat: }1489938120          & \textbf{Location: }Shenzhen, China \\
    \textbf{Email: }Soofjan1489938120@gmail.com & \textbf{Availability: }\textbf{2 Weeks} \\
    \textbf{Education: }Bachelor's Degree (Full-time) & \textbf{Preference: }No Outsource \\
\end{tabular}
\end{center}

\section{\faCogs\ Technical Skills}
\begin{itemize}[parsep=0.3ex]
    \item \textbf{Languages \& Frameworks}: Expert in Go (Gin, Gorm) with deep understanding of keywords, concurrency, GMP scheduling, and memory management; experienced with Vue and multi-platform adaptation.
    \item \textbf{Storage \& Caching}: Proficient in MySQL (InnoDB, B+ Tree, locks, ACID, isolation levels, MVCC); expert in Redis internals including eviction policies, persistence, and caching strategies.
    \item \textbf{Middleware}: Experienced with NSQ architecture, capable of handling message loss and duplicate consumption; familiar with choosing between Kafka and RocketMQ for different scenarios.
    \item \textbf{Tools \& Networking}: Proficient in Git/Linux development environments; solid foundation in TCP/IP, HTTP/HTTPS; highly proficient in using Cursor AI tools for development.
\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Guangzhou University} \quad B.Eng. in Computer Science and Technology}{Sep 2019 -- Jun 2023}
CET-6 (Score: 602), Silver Medal in National Undergraduate Algorithm Design and Programming Challenge.

\section{\faSuitcase\ Work Experience}
\datedsubsection{\textbf{Software Engineer @ Huiwei Intelligence Technology Co., Ltd.}}{May 2023 -- Present}

\paragraph*{Private Cloud Storage System (NAS) Development}

\begin{itemize}

    \item \textbf{Cloud Infrastructure}:
    \begin{itemize}
        \item Led the design of NAT traversal architecture, standardized communication protocols between clients, servers, cloud, and traversal nodes, ensuring stable access in complex network environments.
        \item Integrated NSQ message queue for asynchronous event decoupling, increasing throughput by 1.6x and reducing average latency under high concurrency by approximately 50\%.
        \item Implemented dual-layer encryption (AES+RSA at application layer, TLS at transport layer) to secure credentials and sensitive data in transit.
    \end{itemize}

    \item \textbf{Intelligent Document Center}:
    \begin{itemize}
        \item Migrated the search engine from Elasticsearch to Bleve for memory-constrained environments, integrating with GPT for rapid full-text and multi-dimensional search.
        \item Designed a block-based indexing strategy and search result aggregation algorithm, solving memory exhaustion issues during large document indexing, reducing peak heapInuse by over 76\%.
    \end{itemize}
    
    \item \textbf{File Indexing \& Sync System}:
    \begin{itemize}
        \item Developed a custom BFS+Queue architecture to replace fsnotify for file monitoring, reducing memory overhead by over 90\% in massive file scenarios.
        \item Decoupled sync logic from storage and I/O via interface abstraction and Functional Options patterns, enabling high-cohesion cross-project integration.
    \end{itemize}
    
    \item \textbf{Other Projects}:
    \begin{itemize}
        \item AI Album: Implemented JNI-based tag classification on RKNN; applied DBSCAN for unsupervised face clustering (10K+ faces) with dynamic center updates, reaching 97.3\% accuracy.
        \item Mitigated high-concurrency traffic impacts using rate limiting and the Ristretto caching library, achieving an 85\% cache hit rate for core interfaces and reducing response time by 90ms.
        \item Developed and maintained Docker, Virtual Machine, and Webdav projects, providing a comprehensive NAS ecosystem.
    \end{itemize}

\end{itemize}

\end{document}